\pkg{digiRhythm}: an \proglang{R} package for rhythmicity assessment using the degree of functional coupling

### 2023-06-01 jstatsoft/article.Rnw
Marianne's changes

%% -- Summary/conclusions/discussion -------------------------------------------

@@

The package enables the calculation of rhythmicity from activity data. To date, this is purely a computation of activity patterns that have been correlated with physiological factors in previous studies. This indicator can be calculated from any type of regularly measured time series data, if they are brought in a suitable format, which can be assessed with the  \fct{is\_dgm\_friendly} function. However, we have no evidence if these activity patterns are intrinsically (such as going to sleep) or extrinsically (such as waking up to an alarm) motivated. Such extrinsic factors could affect rhythmic activity patterns and blur physiological rhythmicity patterns. To date, the package provides the option to exclude extrinsically structured time spans from the analysis. However, in order to increase the understanding of rhythmicity  future studies should investigate how these extrinsic factors affect rhythmicity calculations.

@@

>>>>

% Summary/conclusions/discussion

@@

%pacckage enables computation of any activity data
The \pkg{digiRhythm} package enables the calculation of rhythmicity from any activity data. This indicator can be calculated from any type of regularly measured time series data, if the data are prepared in a suitable format. The suitability of the format can be assessed with the  \fct{is\_dgm\_friendly} function. To date, this is purely a computation of activity patterns, resulting the in the DFC. This measure has been correlated with physiological functions in previous studies.

% Scope of DFC application
The computation of rhythmicity allows to gain further insight into an organisms harmonic patterns. Organisms in a good physiological state will present harmonic locomotory patterns, whereas this rhythmicity desynchronizes as a result of physiological events. Simply spoken, an organism will follow the same patterns of locomotion as long as they are in a good physiological and psychological state, whereas these patterns will deviate in the face of dysfunctions. In the past these rhythmic patterns have been discussed with regard to the psychological state of a humans, where psychological challenges, such as bipolar disorders or depression have been associated with the desynchronization of rhythmic patterns (\cite{sabet2021the}).
%Limitation of DFC computation

However, we have no evidence if these activity patterns are intrinsically (such as going to sleep) or extrinsically (such as waking up to an alarm) motivated. Such extrinsic factors could affect rhythmic activity patterns and blur physiological rhythmicity patterns. To date, the package provides the option to exclude extrinsically structured time spans from the analysis. However, in order to increase the understanding of rhythmicity  future studies should investigate how these extrinsic factors affect rhythmicity calculations.

@@

<<>>=

@
